\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-09 paper/main.tex
u

\usepackage{multirow}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

%% macros
\newcommand{\tname}{BugsInDLLs}
\newcommand{\jax}{JAX}
\newcommand{\torch}{PyTorch}
\newcommand{\tf}{Tensorflow}
\newcommand{\numbugs}{115}

@@

Challenges...

@@

>>>>

\usepackage{multirow}
\usepackage{xcolor}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

%% macros
\newcommand{\Fix}[1]{\textbf{[[}\textcolor{red}{#1}\textbf{]]}}
\newcommand{\tname}{BugsInDLLs}
\newcommand{\jax}{JAX}
\newcommand{\torch}{PyTorch}
\newcommand{\tf}{Tensorflow}
\newcommand{\numbugs}{115}

@@

\sloppy Serveral important application domains (e.g., transportation,
medical diagnosis, software development) use AI to optimize some
element of their business process. Deep Learning libraries~(DLLs)
(e.g., \jax, \torch{}, and \tf{}) provide the building blocks for the
AI components of these applications.  Unfortunately, as any piece of
software, these libraries contain bugs. An impressive number of
techniques have been recently proposed to find bugs in these
libraries~\Fix{cite 10+ fuzzing papers here}, however we observe that
the evaluation of these techniques do \emph{not} use a reference set
of reproducible bugs to evaluate their effectiveness. The lack of
evaluation standards is an obstacle to evaluate progress in this
important field.

This paper presents \tname, a database of curated reproducible bugs to
enable credible evaluation of DLL testing techniques.  Our dataset
currently consists of \numbugs{} environments to reproduce bugs across
three popular DLL libraries, namely, \jax, \tf, and \torch.

\Fix{...}

@@

\section{Methodology}
\subsection{DLL and Bug Selection}
\subsection{Reproducing Bugs}
\subsection{}

\section{\tname: Database of Bugs in DLLs}
\subsection{Bug Interface}
\subsection{Test Oracle}
\subsection{Usage and Setup}

\section{\tname: Use cases}

\subsection{Evaluating DLL testing techniques}
\subsection{Fault Detection}
\subsection{Program Repair}

\section{Related Work}

\section{Conclusion and Future Work}
